Compilation and Backend-Independent Vectorization for Multi-Party Computation

### 2022-05-01 overleaf/results.tex
add inner product and biometric graphs

\begin{figure*}[htbp]
\centering
\include{graphs/lan/all-hist-OnlineSetupTimesec}
\caption{Circuit Evaluation Time (Setup + Online) of Benchmarks}
\label{fig:graph_all_eval_time}
\end{figure*}

@@

- Discuss inner product and biometric in detail on LAN
- Discuss their comparison (Time) with WAN

\begin{figure*}[htbp]
\centering
\include{graphs/lan/all-hist-CommunicationMiB}
\caption{Communication Size of Benchmarks}
\label{fig:graph_comm_size_time}
\end{figure*}

\begin{figure*}[htbp]
\centering
\include{graphs/lan/all-hist-CircuitGenerationTimesec}
\caption{Circuit Generation Time of Benchmarks}
\label{fig:graph_circ_gen_time}
\end{figure*}

\begin{figure*}[htbp]
\centering
\include{graphs/lan/all-hist-TotalGates}
\caption{Number of Gates of Benchmarks}
\label{fig:graph_total_gates}
\end{figure*}

\begin{figure*}[htbp]
\centering
\include{graphs/lan/all-hist-OnlineTimesec}
\caption{Online Time of Benchmarks}
\label{fig:graph_online_time}
\end{figure*}

\begin{figure*}[htbp]
\centering
\include{graphs/lan/all-hist-SetupTimesec}
\caption{Setup Time of Benchmarks}
\label{fig:graph_setup_time}
\end{figure*}

>>>>

\begin{figure*}[htbp]
\centering
%\resizebox{7in}{!}{\input{graphs/lan/all-hist-OnlineSetupTimesec}}
\input{graphs/lan/all-hist-OnlineSetupTimesec}
\caption{Circuit Evaluation Time (Setup + Online) of Benchmarks}
\label{fig:graph_all_eval_time}
\end{figure*}

@@

- Discuss inner product and biometric in detail on LAN

\begin{figure}[htbp]
\centering
\resizebox{3.6in}{!}{\input{graphs/lan/biometric-hist-OnlineSetupTimesec}}
\caption{Circuit Evaluation Time for Biometric Matching, x-axis lists database size}
\label{fig:graph_biometric_eval_time}
\end{figure}

\begin{figure}[htbp]
\centering
\resizebox{3.6in}{!}{\input{graphs/lan/inner_product-hist-OnlineSetupTimesec}}
\caption{Circuit Evaluation Time for Inner Product, x-axis lists database size}
\label{fig:graph_inner_product_eval_time}
\end{figure}

- Discuss their comparison (Time) with WAN

\begin{figure*}[htbp]
\centering
\input{graphs/lan/all-hist-CommunicationMiB}
\caption{Communication Size of Benchmarks}
\label{fig:graph_comm_size_time}
\end{figure*}

\begin{figure*}[htbp]
\centering
\input{graphs/lan/all-hist-CircuitGenerationTimesec}
\caption{Circuit Generation Time of Benchmarks}
\label{fig:graph_circ_gen_time}
\end{figure*}

\begin{figure*}[htbp]
\centering
\input{graphs/lan/all-hist-TotalGates}
\caption{Number of Gates of Benchmarks}
\label{fig:graph_total_gates}
\end{figure*}

\begin{figure*}[htbp]
\centering
\input{graphs/lan/all-hist-OnlineTimesec}
\caption{Online Time of Benchmarks}
\label{fig:graph_online_time}
\end{figure*}

\begin{figure*}[htbp]
\centering
\input{graphs/lan/all-hist-SetupTimesec}
\caption{Setup Time of Benchmarks}
\label{fig:graph_setup_time}
\end{figure*}
